---
title: "Insurance Data"
output:
  html_document:
     highlight: zenburn
     theme: lumen
     df_print: paged
     fig_align: center
     code_folding: hide
  md_document:
    variant: markdown_github
---

```{r, include=FALSE, echo=FALSE}
library(CASdatasets)
library(tidyverse)
```

```{r}
data(ausNLHYClaimByState)

aus <- ausNLHYClaimByState %>%
    as_tibble()

aus %>%
    head()

data(nzcathist)

nz <- nzcathist %>%
    as_tibble()

nz %>% head()
```

## For AUS data

- **Class** : Class of business.
- **NSWACTYYYYMM** : New South Wales / Australian Capital Territory for year YYYY.
- **VICYYYYMM** : Victoria in year YYYY reported onDate YYYYMM.
- **QLDYYYMM** : Queensland in year YYYY reported onDate YYYYMM.
- **SAYYYYMM** : South Australia in year YYYY reported onDate YYYYMM.
- **WAYYYYMM** : Western Australia in year YYYY reported onDate YYYYMM.
- **TAYYYYMM** : Tasmania in year YYYY reported onDate YYYYMM.
- **NTYYYYMM** : Northern Territory in year YYYY reported onDate YYYYMM.
- **TotalYYYYMM** : Total in year YYYY reported onDate YYYYMM.

Data is in values of millions of Australian dollars (AUD)

## For NZ data

nzcathist is a data frame of 9 columns:

- **Year** : numeric for the Year.
- **Quarter** : numeric for the quarter of the year.
- **Date** : character string for the date.
- **FirstDayaDateobject** : for the first day of natural catastrophe.
- **Event** : character string describing the event.
- **Type** : factor describing the event type among the list:
   "Cyclone"
   "Earthquake"
   "Flood"
   "Flood, Storm"
   "Hailstorm"
   "Other"
   "Power outage"
   "Storm"
   "Tornado"
   "Weather"
- **Location** character string describing the location.
- **OriginalCostOriginal** cost in million of Australian dollars (NZD).
- **NormCost2011Normed** cost in million of 2011 New Zealand dollars (NZD).
- **NormCost2014Normed** cost in million of 2014 New Zealand dollars (NZD)
